A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$ methods

### 2025-03-24 paper_v02/article.tex
updating tests

\color{red}Inserir parágrafo com citações de artigos que aplicam o $\rho_{DCCA}$\color{black}

@@

\begin{table}[h]
  \label{tab:time}
  \centering
  \caption{Elapsed Time Comparison}
  \begin{tabular}{@{}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{}}
    \hline
    Package & Implementation & Elapsed Time(s) & Percentage Increase \\
    \hline
    Zebende & Zig (opt) & 27.52  & - \\
    Zebende & Zig (basic) & 42.03 & 52.7\% \\
    DCCA & Python & 370.54 & 1239.4\% \\
    DCCA & R-Java & 1987.67 & 7202.4\% \\
    Zebende & Python & 2415.94 & 8803.4\% \\
    DFA & R & 20173.13 & 73,011.4\% \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{
    figs/elapsed_tws.png}
  \caption{\label{fig:elapsed_tws}Elapsed Time Comparison for Different Implementations}
\end{figure}

>>>>

The method was statistically validated~\citep{PhysRevE.84.066118}, applied to climate data~\cite{vassolerZebende2012}, financial data\citep{Wang2013, Guedes2017, Ferreira2018}, electroencephalogram recorded data \citep{Oliveira2023}, among others. Statistical criteria for evaluating the relevance of the results were also developed~\cite{Guedes2018,Guedes2018a}.

@@

\begin{table}[h]
  \label{tab:time}
  \centering
  \caption{Elapsed Time Comparison with four series}
  \begin{tabular}{@{}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{\hspace{1.0cm}}l@{}}
    \hline
    Package & Implementation & Elapsed Time(s) & Percentage Increase \\
    \hline
    Zebende & Zig (opt) & 27.52  & - \\
    Zebende & Zig (basic) & 42.03 & 52.7\% \\
    DCCA & Python & 370.54 & 1239.4\% \\
    DCCA & R-Java & 1987.67 & 7202.4\% \\
    Zebende & Python & 2415.94 & 8803.4\% \\
    DFA & R & 20173.13 & 73,011.4\% \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[h!]
  \centering
  \includegraphics{
    figs/elapsed_tws.png}
  \caption{\label{fig:elapsed_tws}Elapsed Time Comparison for Different Implementations (four series)}
\end{figure}
